Incentivizing Exploration with Unbiased History

### 2018-11-01 model.tex
Minor edits in model.

Further, we focus on disclosure policies that are \emph{transitive}, in the following sense:
\[ t'\in S_t \Rightarrow S_{t'}\subset S_t
    \qquad \text{for all rounds $t,t'\in [T]$}. \]
In words, if an agent observes the outcome for some previous agent, then she observes the entire message revealed to that agent.

A transitive unbiased-history policy can be represented as an undirected graph, where nodes correspond to rounds, and any two rounds $t'<t$ are connected if and only if $t'\in S_t$ and there is no intermediate round $t''$ with
    $t'\in S_{t''}$ and $t''\in S_t$.
This graph is henceforth called the \emph{information flow graph} of policy $\pi$, or \emph{info-graph} for short. We assume that it is common knowledge.

>>>>

Further, we focus on disclosure policies that are \emph{transitive}, in the following sense:
\[ t\in S_{t'} \Rightarrow S_t\subset S_{t'}
    \qquad \text{for all rounds $t,t'\in [T]$}. \]
In words, if agent $t'$ observes the outcome for some previous agent $t$, then she observes the entire message revealed to that agent. In particular, agent $t'$ does not need to second-guess which message has caused agent $t$ to choose action $a_t$.

A transitive unbiased-history policy can be represented as an undirected graph, where nodes correspond to rounds, and any two rounds $t<t'$ are connected if and only if $t\in S_{t'}$ and there is no intermediate round $t''$ with
    $t\in S_{t''}$ and $t''\in S_{t'}$.
This graph is henceforth called the \emph{information flow graph} of the policy, or \emph{info-graph} for short. We assume that this graph is common knowledge.
